The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-03 paper.tex
update

To this end, this work consider a dense thin disk of interstellar medium\
around a jet source, in an attempt to remedy the symmetry problem of the Galactic bubbles.\

@@

This paper is organized as follows. We introduce

\section{Methodology}

  We used the GPU-accelerated special relativistic hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
  National Taiwan University\
  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
  to carry out the simulations of the Fermi and eROSITA bubbles by CR and relativistic fluid injections from the GC.

@@

\section{Results}

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disk (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disk has an insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disk\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear associated with the disk, and without the disk, the outer bubbles will be tilted,
             indicating the dense disk is crucial for\
             the axis-symmetrically outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

@@

\section{conclusions}

>>>>

To this end, this work introduces a dense thin disk of interstellar medium\
around a jet source, in an attempt to remedy the symmetry problem of the Galactic bubbles.\
The thin disk contains a reservoir of dense molecular/atomic gas, resulting in\

@@

This paper is organized as follows.\
In Section \ref{Methodology}, we describe the numerical techniques and initial conditions employed.\
We directly compare the morphology of the Galactic bubbles with observation,\
and also show the simulated gamma-ray and microwave spectra compared with observations\
in Section \ref{Results}.
Finally, we summarize our findings in Section \ref{Conclusions}.

\section{Methodology}
\label{Methodology}
  We used the GPU-accelerated special relativistic hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
  National Taiwan University\
  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
  to carry out the simulations of the Fermi and eROSITA bubbles by CR and relativistic fluid injections from the GC.

@@

\section{Results}
\label{Results}
  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disk (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disk has an insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disk\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear associated with the disk, and without the disk, the outer bubbles will be tilted,
             indicating the dense disk is crucial for\
             the axis-symmetrically outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

@@

\section{Conclusions}
\label{Conclusions}
